How Toronto's homeless death toll over the years shows the dangers of addiction's epidemic?

### 2024-01-23 outputs/paper/paper.qmd
edited tables in the paper

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

# Data {#sec-data}
col.names = c("Year of Death", "Cause of Death", "Age Group", "Gender", "Count", "Cause Group"),
Some of our data is of penguins (@fig-bills), from @palmerpenguins.
```{r}
#| warning: false
#| message: false

file_path <- "../../inputs/data/raw_data.csv"
toronto_homeless_death <- read.csv(file_path)
sample_data <- head(toronto_homeless_death, 6)
table_output <- kable(sample_data,

                      caption = "Sample Table for Causes of Death")
# Print the table
cat(table_output)
```

@@

#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("outputs/data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")

@@

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

@@

Our results are summarized in @tbl-modelresults.
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

first_model <-
  readRDS(file = here::here("outputs/models/first_model.rds"))
```{r}

```
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```{r}

@@

# Appendix {-}

@@

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows... 
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

@@

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```{r}

@@

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

@@

plot(first_model, "rhat")
```{r}

>>>>

---
title: "How Toronto's homeless death toll over the years shows the dangers of addiction's epidemic?"
subtitle: "Data analysis of homeless deaths in Toronto from 2017 to 2023"
author: 
  - Shipeng Zhang
thanks: "Code and data are available at: LINK."
date: 2024-01-22
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
editor: 
  markdown: 
    wrap: 72
---

@@

# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| warning: false
#| message: false
#| echo: false

file_path <- "../../inputs/data/raw_data.csv"
toronto_homeless_death <- read.csv(file_path)
toronto_homeless_death <- dplyr::select(toronto_homeless_death, -X_id)           
sample_data <- head(toronto_homeless_death, 6)
knitr::kable(sample_data,'markdown',col.names = c("Year of Death", "Cause of Death", "Age Group", "Gender", "Count"),align = 'c',

                      caption = "Sample Table for Causes of Death")
  # Print the table

@@

#\| label: fig-planes #\| fig-cap: Relationship between wing length and
width #\| echo: false #\| warning: false #\| message: false

analysis_data \<- read_csv(here::here("outputs/data/analysis_data.csv"))

analysis_data \|\> ggplot(aes(x = width, y = length)) + geom_point(alpha
= 0.8) + theme_minimal() + labs(x = "Wing width (mm)", y = "Wing length
(mm)")

@@

```{=tex}
\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}
```
We run the model in R [@citeR] using the `rstanarm` package of
@rstanarm. We use the default priors from `rstanarm`.

@@

Our results are summarized in @tbl-modelresults. #\| echo: false #\|
eval: true #\| warning: false #\| message: false

@@

first_model \<- readRDS(file =
here::here("outputs/models/first_model.rds"))

#\| echo: false #\| eval: true #\| label: tbl-modelresults #\| tbl-cap:
"Explanatory models of flight time based on wing width and wing length"
#\| warning: false

modelsummary::modelsummary( list( "First model" = first_model ),
statistic = "mad", fmt = 2 )

@@

# Appendix {.unnumbered}

@@

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the
prior. This shows... #\| eval: true #\| echo: false #\| message: false
#\| warning: false #\| label: fig-ppcheckandposteriorvsprior #\|
layout-ncol: 2 #\| fig-cap: "Examining how the model fits, and is
affected by, the data" #\| fig-subcap: \["Posterior prediction check",
"Comparing the posterior with the prior"\]

@@

posterior_vs_prior(first_model) + theme_minimal() +
scale_color_brewer(palette = "Set1") + theme(legend.position =
"bottom") + coord_flip()

@@

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests... #\|
echo: false #\| eval: true #\| message: false #\| warning: false #\|
label: fig-stanareyouokay #\| fig-cap: "Checking the convergence of the
MCMC algorithm" #\| fig-subcap: \["Trace plot", "Rhat plot"\] #\|
layout-ncol: 2

@@

plot(first_model, "rhat")
